### 2018-05-02 paper/message-passing-design.tex
minor

\begin{figure}[t]
  \includegraphics[width=\linewidth]{figures/file_exchange_v2.pdf}
  \caption{\label{fig:file-exchange}A schematic of the creation and usage of PORs between Alice and Bob's e-squads.}
\end{figure}

@@

      % \State $H\gets \ExtendRoute[H_\rdv, L, \theta]$
      % \State $D\concat C_H\gets H_\rdv$
      % \For{$d\in D$}
      %   \Comment{Uniformly randomly chosen}
      %   \If{$d\method \Fwd[C_H, m] \neq \bot$}
      %     \State \Return $\top$
      %   \EndIf
      % \EndFor
      % \State \Return $\bot$
    \EndFunction
  \end{algorithmic}
  %\end{minipage}}

  % \vspace{0.3em}
  % %\framebox{\begin{minipage}{0.96\linewidth}
  % \begin{algorithmic}[1]
  %   % \Require{%
  %   %   $H$ is a header of the form \(D\concat H'\) or \(D\concat \top\), where 
  %   %   \(D\) is a set of device addresses.
  %   %   $\pk_D$ is the public key of device set $D$.
  %   %   $L$ is the length of the route,
  %   %   $\theta$ is the threshold of probability of failure.%
  %   % }
  %   \Function{\ExtendRoute}{$\mathcal{H}, l$}
  %     \If{$L\leq 0$}
  %       \State \Return $H$
  %     \EndIf
  %     \State $D\gets \CreateOnionLayer[\theta]$
  %     \State $H\gets D\concat \DeBEenc[\mpk, D, H]$
  %     \State \Return $\ExtendRoute[H, L-1, \theta]$
  %   \EndFunction
  % \end{algorithmic}

@@

% subsubsection exchanging_a_file (end)
\newcommand{\messagesize}{\ensuremath{s_m}}
\newcommand{\filesize}{\ensuremath{s_{fc}}
\newcommand{\headersize}{\ensuremath{s_{\mathcal{H}}}}

@@

\commentAL{Is it good?}
In \name, whole messages, headers and file chunks are considered having a fixed size.
In reality, the message size \messagesize is indeed fixed to prevent \name from message size analysis attacks,
but the header size \headersize is variable, depending on the number of layers and the number of devices per layer.
File chunks would then have a size  inversely proportional to \headersize : $\filesize = \messagesize - \headersize$.

>>>>

\begin{figure}[t]
  \includegraphics[width=\linewidth]{figures/file_exchange.pdf}
  \caption{\label{fig:file-exchange}A schematic of the creation and usage of PORs between Alice and Bob's e-squads.}
\end{figure}

@@

      \STATE $H\gets \ExtendRoute[H_\rdv, L, \theta]$
      \State $D\concat C_H\gets H_\rdv$
      \For{$d\in D$}
        \Comment{Uniformly randomly chosen}
        \If{$d\method \Fwd[C_H, m] \neq \bot$}
          \State \Return $\top$
        \EndIf
      \EndFor
      \State \Return $\bot$
    \EndFunction
  \end{algorithmic}
  %\end{minipage}}

  % \vspace{0.3em}
  % %\framebox{\begin{minipage}{0.96\linewidth}
  \begin{algorithmic}[1]
    \Require{%
      $H$ is a header of the form \(D\concat H'\) or \(D\concat \top\), where 
      \(D\) is a set of device addresses.
      $\pk_D$ is the public key of device set $D$.
      $L$ is the length of the route,
      $\theta$ is the threshold of probability of failure.%
    }
    \Function{\ExtendRoute}{$\mathcal{H}, l$}
      \If{$L\leq 0$}
        \State \Return $H$
      \EndIf
      \State $D\gets \CreateOnionLayer[\theta]$
      \State $H\gets D\concat \DeBEenc[\mpk, D, H]$
      \State \Return $\ExtendRoute[H, L-1, \theta]$
    \EndFunction
  \end{algorithmic}

@@

% subsubsection exchanging_a_file (end)
\newcommand{\messagesize}{\ensuremath{s_m}}
\newcommand{\filesize}{\ensuremath{s_{fc}}}
\newcommand{\headersize}{\ensuremath{s_{\mathcal{H}}}}

@@

In \name, whole messages, headers and file chunks are considered having a fixed size.
In reality, the message size \messagesize is indeed fixed to prevent \name from message size analysis attacks,
but the header size \headersize is variable, depending on the number of layers and the number of devices per layer.
File chunks would then have a size  inversely proportional to \headersize : $\filesize = \messagesize - \headersize$.
